\normalfont\spacedallcaps{The economic consequences of the different attitudes of a policy maker: a combined epidemiological-econometric study}

### 2021-03-08 Manuscript/manuscript.tex
PUB

\textcolor{blue}{Appliances}/radios/televisions and tape recorders, \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware,  \textcolor{blue}{Games}/toys/sports and camping articles. The choice to use the selling as a parameter for the evaluation of the lock-down lies on the fact that with them it is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa). Such calculation may be considered as a future outlook of this work}. Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods, \textcolor{blue}{Real estate} activities, rental, IT, research, business services\footnote{On contrary with respect to the category Equipment for information technology of selling, here the IT contribution is overwhelmed by the other ones (e.g Real Estate), making it negligible. Thus, in this case we included the whole sector}. In this case the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them the production was also banned by law during the lock-down \footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020. Contrary with respect to the first wave, the lock-down did not banned by law the production. As told previously this option was not considered by the authors since the most of the economic data were available, with the temporal resolution considered in this work, only at national level.}. For the empirical evaluation of the impact on selling and unemployment benefit we performed a Difference-In-Difference (DID) where multiple times where considered as used in Refs. \cite{draca2011panic} and \cite{wooldridge2012introductory}. The following regression was performed: 

@@

For each sales category we run the regression reported in the Eq.  \ref{DID-eq} on de-seasoned data reported in Fig \ref{Selling_plots} and \ref{Selling_plots_II}.  The coefficients obtained are reported in Tab.  \ref{selling_DID_table_delta}.  As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.  As consequence this pre-trend,  compared to the lock-down effect,  can be considered negligible.

@@

\end{tabular}
\label{selling_DID_table_delta}
\end{table}
\end{landscape}
\newpage

>>>>

\textcolor{blue}{Appliances}/radios/televisions and tape recorders, \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware,  \textcolor{blue}{Games}/toys/sports and camping articles. The choice to use the selling as a parameter for the evaluation of the lock-down lies on the fact that with them it is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa). Such calculation may be considered as a future outlook of this work}. Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.  In this case the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them the production was also banned by law during the lock-down \footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020. Contrary with respect to the first wave, the lock-down did not banned by law the production. As told previously this option was not considered by the authors since the most of the economic data were available, with the temporal resolution considered in this work, only at national level.}. For the empirical evaluation of the impact on selling and unemployment benefit we performed a Difference-In-Difference (DID) where multiple times where considered as used in Refs. \cite{draca2011panic} and \cite{wooldridge2012introductory}. The following regression was performed: 

@@

For each sales category we run the regression reported in the Eq.  \ref{DID-eq} on de-seasoned data reported in Fig \ref{Selling_plots} and \ref{Selling_plots_II}.  The coefficients obtained are reported in Tab.  \ref{selling_DID_table_delta}.  As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.  As consequence this pre-trend,  compared to the lock-down effect,  can be considered negligible.  In order to make a further control,  a placebo test was performed by choosing timing before the pandemic of COVID19.  As illustrated in the Supporting Info,  this test was successful.  We than run the DID regression also for the subsidies: the plot of the data and the DID coefficients are reported in Fig \ref{CIG_sector_plots} and in Tab \ref{CIG_DID}.  Also in this case the placebo test were successfully performed.

@@

\end{tabular}
\label{selling_DID_table_delta}
\end{table}
\end{landscape}

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_Manifattura.pdf}
         \caption{Subsidies paid for manufacture} 
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_Commercio.pdf}}
         \caption{Subsidies paid for trade}
     \end{subfigure}
          \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_Costruzioni.pdf}
         \caption{Construction}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \includegraphics[width=\textwidth]{Figures/CIG_TOT.pdf}}
          \caption{Total}
     \end{subfigure}
\caption{Comparison between the ordinary subsides (blue)   vs the extraordinary ones (renovation red and purple solidarity) for a selected set of sectors and the overall total.  The dashed lines represent the different timing  and intensity for the lock-down:  red for high, orange medium and green for low.  }
\label{CIG_sector_plots}
\end{figure}

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\delta$ cofficients as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) according to equation \ref{DID-eq} \\ for the different lock-down timings. The values of the  intercept ($\alpha$), C and T$_{i}$ are provided in the Supporting Info. 
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
{\color[HTML]{343434} Total}        & 706    & 3     & 199.5  & 217    & 3     & 61.48 & 144    & 3     & 40.72 \\ \hline
{\color[HTML]{343434} Manufacture}  & 494    & 3     & 158.56 & 162    & 3     & 52    & 111    & 3     & 35.7  \\ \hline
{\color[HTML]{343434} Trade}        & 16.4   & 0.24  & 66.10  & 3.72   & 0.24  & 15.00 & 2.92   & 0.24  & 11.78 \\ \hline
{\color[HTML]{343434} Construction} & 134    & 0.87  & 153.10 & 29     & 0.87  & 33.13 & 14     & 0.87  & 16.41 \\ \hline
\label{CIG_DID}
\end{tabular}
\end{table}
\end{landscape}

\clearpage
\newpage
